% Preamble
% ---
\documentclass{article}

% Packages
% ---
\usepackage{amsmath} % Advanced math typesetting
\usepackage[utf8]{inputenc} % Unicode support (Umlauts etc.)
\usepackage[english]{babel}
\usepackage{hyperref} % Add a link to your document
\usepackage{graphicx} % Add pictures to your document
\usepackage{listings} % Source code formatting and highlighting
\usepackage{csquotes}
\usepackage[
backend=biber,
style=alphabetic,
sorting=ynt
]{biblatex}

\addbibresource{report.bib}
\setlength{\parskip}{1em}

% Main document
% ---
\begin{document}
% Set up the maketitle command
\author{Eric Conlon}
\title{Classifying Street View House Numbers with Deep Learning}
\date{2016-11-9}

\maketitle{} % Generates title

\tableofcontents{} % Generates table of contents from sections

\section{Introduction}

Character recognition is a classic computer vision problem with many interesting variants. Even restricting ourselves to 10-digit classification still leaves much room for uncertainty and creativity. The Street View House Numbers dataset (SVHN) poses a such a classification problem that is generally considered to be tougher than the common MNIST dataset.

In this report I explain some simple approaches to classification of both datasets with both conventional and deep learning methods. The conventional baseline here is a Support Vector Classifier using Histogram of Gradients features, and the deep learning challenger is a Convolutional Neural Network. These solutions may not rank among the state of the art, but it is my hope that the details of end-to-end architecture and practical engineering considerations will prove to be interesting.

\section{Datasets}

MNIST is a classic labeled dataset consisting of single handwritten digits (0-9) that have been extensively processed. Each digit is centered alone within a 28x28 grid, and all pixel intensities are set to 0 (background) and 1 (foreground). These images don't require common preprocessing techniques such as rescaling, contrast enhancement, or whitening to be immediately useful. There are around 60,000 training examples and 10,000 test examples.

SVHN is a labeled dataset that comes from images of house numbers collected by Google's Street View project. The digits have a wide variety of foreground and background colors, textures, noise, distractions, orientations, and scales. There are two formats provided: the first includes raw images with sets of bounding rectangles, and the second includes a more MNIST-like centered digits. The models here consume only the second format, but I will say more about this classifiers applicability to the first. Overall, this dataset contains almost 8 times more examples than MNIST.

\section{Design} 

\section{Exploration and Evaluation}

\section{Conventional Solution}

\section{Deep Learning Solution}

\section{Conclusion}

\printbibliography[heading=bibintoc,title={References}]

\end{document}